---
title: "Extraction"
date: "2026-08-07"
output: html_document
---

# Requirements

## + Libraries:

- Having a Warcraft Logs account -> Settings
- Create a v2 API Key
    .Copy your client ID
    .Copy your client secret

```{r}
remotes::install_github("jruizcabrejos/wclR")
library(wclR)
library(tidyverse)
```

## + API Key

```{r}
Sys.setenv(
  Sys.getenv("WCLR_CLIENT_ID"),
  Sys.getenv("WCLR_CLIENT_SECRET")
)
```

# Get data

## + Reports

```{r}
# df_reports <- wclR::wcl_reports(1056,pages=1:25)

df_reports <- read_csv("./data/df_reports.csv")
```

```{r}
V_REPORTS <- df_reports$logID
N_REPORTS <- nrow(df_reports)
```

## + Fights

```{r}
df_fights <- data.frame()

for(i in 1:N_REPORTS){
  
  df_fights <- bind_rows(df_fights,
                         wcl_fights(V_REPORTS[i]))
  
  print(i)
  
}

# write_csv(df_fights,"./df_fights.csv")
df_fights <- read_csv("./df_fights.csv")
```

This is a very aggresive filter - Ideally, group composition should be used + use duration rounded to the closest integer.

```{r}
df_fights_clean <- wcl_distinct_fights(
  df_fights,
  by = c(
    "encounterID", "difficulty",
    "size", "kill",
    "bossPercentage", "duration",
    "averageItemLevel")
)
```


```{r}
VALID_ENCOUNTERS <- c(100623, # Hydross the Unstable
                      100624, # The Lurker Below
                      100625, # Leotheras the Blind
                      100626, # Fathom-Lord Karathress
                      100627, # Morogrim Tidewalker
                      100628, # Lady Vashj
                      
                      100730, # Al'ar 
                      100731, # Void Reaver
                      100732, # High Astromancer Solarian
                      100733  # Kael'thas Sunstrider
)

df_fights_clean_2 <- df_fights_clean %>%
  filter(encounterID %in% VALID_ENCOUNTERS)
```


```{r}
df_fights_clean_2 %>%
  group_by(kill) %>%
  summarise(mean_time = mean(duration_s),
            min_time = min(duration_s),
            max_time = max(duration_s))

df_fights_clean_2 %>%
  ggplot() +
  geom_histogram(aes(x=duration_s)) +
  facet_wrap(.~kill) +
  scale_x_continuous(limits=c(0,100))
```

```{r}
df_fights_clean_3 <- df_fights_clean_2 %>%
  filter(!(duration_s<=30 & kill==F))
```


```{r}
V_REPORTS_CLEAN <- df_fights_clean_3 %>% 
  dplyr::select(logID) %>% pull(.) %>% unique(.)
```

From this point onwards, it is more efficient to only look at Kills, not 

## + Events (Innervate)

```{r}
N_FIGHTS<- nrow(df_fights_clean_3)

df_fights_clean_3 %>%
  group_by(kill) %>%
  summarize(n=n())
```

```{r}
df_events <- data.frame()
df_errors <- data.frame()

for (i in 1:N_FIGHTS) {
  i_REPORT <- df_fights_clean_3$logID[i]
  i_FIGHT  <- df_fights_clean_3$fightID[i]
  i_STARTTIME  <- df_fights_clean_3$startTime[i]-10
  i_ENDTIME  <- df_fights_clean_3$endTime[i]+10
  
  res <- NULL
  success <- FALSE
  max_retries <- 2
  attempts <- 0
  
  while (!success && attempts < max_retries) {
    attempts <- attempts + 1
    
    res <- tryCatch(
      expr = {
        wcl_events(
          report_code       = i_REPORT,
          fight_id          = i_FIGHT,
          data_type         = "All",
          hostility_type    = "Friendlies",
          filter_expression = "ability.id = 29166",
          start_time = i_STARTTIME,
          end_time = i_ENDTIME
        )
      },
      error = function(e) {
        if (!exists("df_errors")) {
          df_errors <<- data.frame(
            i         = integer(),
            logID     = character(),
            fightID   = integer(),
            attempt   = integer(),
            error_msg = character(),
            timestamp = POSIXct(),
            stringsAsFactors = FALSE
          )
        }
        
        df_errors <<- dplyr::bind_rows(
          df_errors,
          data.frame(
            i         = i,
            logID     = i_REPORT,
            fightID   = i_FIGHT,
            attempt   = attempts,
            error_msg = e$message,
            timestamp = Sys.time(),
            stringsAsFactors = FALSE
          )
        )
        
        # Return the error object to check the message outside tryCatch
        return(e)
      }
    )
    
    # Check if the result was successful or an error was caught
    if (inherits(res, "error")) {
      perm_error_msg <- "Warcraft Logs GraphQL error: You do not have permission to view this report."
      
      if (grepl(perm_error_msg, res$message, fixed = TRUE)) {
        print(paste0("Permission denied for ", i_REPORT, " - skipping immediately to next report."))
        res <- NULL
        break # Exit while loop and move to next iteration of i
      } else if (attempts < max_retries) {
        print(paste0("Other error on iteration ", i, ". Waiting 50 minutes before retrying (Attempt ", attempts, " of ", max_retries, ")..."))
        res <- NULL
        Sys.sleep(3000)
      } else {
        res <- NULL
      }
    } else if (!is.null(res)) {
      success <- TRUE
    }
  }
  
  if (!is.null(res)) {
    df_events <- dplyr::bind_rows(df_events, res)
  }
  
  print(paste0(i, " out of ", N_FIGHTS, " - ", i_REPORT, " ", i_FIGHT))
}
  
  
  
# write_csv(df_events %>% dplyr::select(-c(classResources)),"./df_events_3.csv")
df_events <- read_csv("./df_events_3.csv")
```


## + Deaths

```{r}
df_events_deaths <- data.frame()
df_errors <- data.frame()

for (i in 1:N_FIGHTS) {
  i_REPORT <- df_fights_clean_3$logID[i]
  i_FIGHT  <- df_fights_clean_3$fightID[i]
  i_STARTTIME  <- df_fights_clean_3$startTime[i]-10
  i_ENDTIME  <- df_fights_clean_3$endTime[i]+10
  
  res <- NULL
  success <- FALSE
  max_retries <- 2
  attempts <- 0
  
  while (!success && attempts < max_retries) {
    attempts <- attempts + 1
    
    res <- tryCatch(
      expr = {
        wcl_events(
          report_code       = i_REPORT,
          fight_id          = i_FIGHT,
          data_type         = "Deaths",
          hostility_type    = "Friendlies",
          # filter_expression = "ability.id = 29166",
          start_time = i_STARTTIME,
          end_time = i_ENDTIME
        )
      },
      error = function(e) {
        if (!exists("df_errors")) {
          df_errors <<- data.frame(
            i         = integer(),
            logID     = character(),
            fightID   = integer(),
            attempt   = integer(),
            error_msg = character(),
            timestamp = POSIXct(),
            stringsAsFactors = FALSE
          )
        }
        
        df_errors <<- dplyr::bind_rows(
          df_errors,
          data.frame(
            i         = i,
            logID     = i_REPORT,
            fightID   = i_FIGHT,
            attempt   = attempts,
            error_msg = e$message,
            timestamp = Sys.time(),
            stringsAsFactors = FALSE
          )
        )
        
        # Return the error object to check the message outside tryCatch
        return(e)
      }
    )
    
    # Check if the result was successful or an error was caught
    if (inherits(res, "error")) {
      perm_error_msg <- "Warcraft Logs GraphQL error: You do not have permission to view this report."
      
      if (grepl(perm_error_msg, res$message, fixed = TRUE)) {
        print(paste0("Permission denied for ", i_REPORT, " - skipping immediately to next report."))
        res <- NULL
        break # Exit while loop and move to next iteration of i
      } else if (attempts < max_retries) {
        print(paste0("Other error on iteration ", i, ". Waiting 50 minutes before retrying (Attempt ", attempts, " of ", max_retries, ")..."))
        res <- NULL
        Sys.sleep(3000)
      } else {
        res <- NULL
      }
    } else if (!is.null(res)) {
      success <- TRUE
    }
  }
  
  if (!is.null(res)) {
    df_events_deaths <- dplyr::bind_rows(df_events_deaths, res)
  }
  
  print(paste0(i, " out of ", N_FIGHTS, " - ", i_REPORT, " ", i_FIGHT))
}
  
  
# write_csv(df_events_deaths,"./df_events_deaths.csv")
df_events_deaths <- read_csv("./df_events_deaths.csv")
```


## + Parses

At this point I should have filtered by logs with deaths/nondeaths.
This procedure could also be done after "Fights" extraction.

```{r}
df_parses <- data.frame()
df_errors <- data.frame()

N_REPORTS_CLEAN <- length(V_REPORTS_CLEAN)

for (i in 1:N_REPORTS_CLEAN) {
  i_REPORT <- V_REPORTS_CLEAN[i]
  
  res <- NULL
  success <- FALSE
  max_retries <- 2
  attempts <- 0
  
  while (!success && attempts < max_retries) {
    attempts <- attempts + 1
    
    res <- tryCatch(
      expr = {
        wcl_report_rankings(
          report_code       = i_REPORT,
          timeframe         = "Historical",
        )
      },
      error = function(e) {
        if (!exists("df_errors")) {
          df_errors <<- data.frame(
            i         = integer(),
            logID     = character(),
            attempt   = integer(),
            error_msg = character(),
            timestamp = POSIXct(),
            stringsAsFactors = FALSE
          )
        }
        
        df_errors <<- dplyr::bind_rows(
          df_errors,
          data.frame(
            i         = i,
            logID     = i_REPORT,
            attempt   = attempts,
            error_msg = e$message,
            timestamp = Sys.time(),
            stringsAsFactors = FALSE
          )
        )
        
        # Return the error object to check the message outside tryCatch
        return(e)
      }
    )
    
    # Check if the result was successful or an error was caught
    if (inherits(res, "error")) {
      perm_error_msg <- "Warcraft Logs GraphQL error: You do not have permission to view this report."
      
      if (grepl(perm_error_msg, res$message, fixed = TRUE)) {
        print(paste0("Permission denied for ", i_REPORT, " - skipping immediately to next report."))
        res <- NULL
        break # Exit while loop and move to next iteration of i
      } else if (attempts < max_retries) {
        print(paste0("Other error on iteration ", i, ". Waiting 50 minutes before retrying (Attempt ", attempts, " of ", max_retries, ")..."))
        res <- NULL
        Sys.sleep(3450)
      } else {
        res <- NULL
      }
    } else if (!is.null(res)) {
      success <- TRUE
    }
  }
  
  if (!is.null(res)) {
    df_parses <- dplyr::bind_rows(df_parses , res)
  }
  
  print(paste0(i, " out of ", N_REPORTS_CLEAN, " - ", i_REPORT))
}
  
  
write_csv(df_parses,"./df_parses.csv")
# df_parses <- read_csv("./df_parses.csv")
```


## + Players

```{r}
df_players_detail <- data.frame()
df_errors <- data.frame()

N_FIGHTS_VALID <- nrow(df_fights_clean_3)

for (i in 1:nrow(df_fights_clean_3)) {
  
  i_REPORT <- df_fights_clean_3$logID[i]
  i_FIGHT  <- df_fights_clean_3$fightID[i]
  
  res <- NULL
  success <- FALSE
  max_retries <- 2
  attempts <- 0
  
  while (!success && attempts < max_retries) {
    attempts <- attempts + 1
    
    res <- tryCatch(
      expr = {
        wcl_player_details(
          report_code       = i_REPORT,
          fight_id = i_FIGHT
          )
      },
      error = function(e) {
        if (!exists("df_errors")) {
          df_errors <<- data.frame(
            i         = integer(),
            logID     = character(),
            attempt   = integer(),
            error_msg = character(),
            timestamp = POSIXct(),
            stringsAsFactors = FALSE
          )
        }
        
        df_errors <<- dplyr::bind_rows(
          df_errors,
          data.frame(
            i         = i,
            logID     = i_REPORT,
            attempt   = attempts,
            error_msg = e$message,
            timestamp = Sys.time(),
            stringsAsFactors = FALSE
          )
        )
        
        # Return the error object to check the message outside tryCatch
        return(e)
      }
    )
    
    # Check if the result was successful or an error was caught
    if (inherits(res, "error")) {
      perm_error_msg <- "Warcraft Logs GraphQL error: You do not have permission to view this report."
      
      if (grepl(perm_error_msg, res$message, fixed = TRUE)) {
        print(paste0("Permission denied for ", i_REPORT, " - skipping immediately to next report."))
        res <- NULL
        break # Exit while loop and move to next iteration of i
      } else if (attempts < max_retries) {
        print(paste0("Other error on iteration ", i, ". Waiting 50 minutes before retrying (Attempt ", attempts, " of ", max_retries, ")..."))
        res <- NULL
        Sys.sleep(3450)
      } else {
        res <- NULL
      }
    } else if (!is.null(res)) {
      success <- TRUE
    }
  }
  
  if (!is.null(res)) {
    df_players_detail <- dplyr::bind_rows(df_players_detail , res)
  }
  
  print(paste0(i, " out of ", N_FIGHTS_VALID, " - ", i_REPORT))
}
  
  
write_csv(df_players_detail,"./df_players_detail.csv")
# df_players_detail <- read_csv("./df_players_detail.csv")


```


## + Events (Buffs)

Loop number 5778 messed up during the initial extraction. This log therefore has been excluded in the final analysis:
pfQALavGTBzngxXq

```{r}
df_events_buffs <- data.frame()
df_errors <- data.frame()

for (i in 1:N_FIGHTS) {
  i_REPORT <- df_fights_clean_3$logID[i]
  i_FIGHT  <- df_fights_clean_3$fightID[i]
  i_STARTTIME  <- df_fights_clean_3$startTime[i]-10
  i_ENDTIME  <- df_fights_clean_3$endTime[i]+10
  
  res <- NULL
  success <- FALSE
  max_retries <- 2
  attempts <- 0
  
  while (!success && attempts < max_retries) {
    attempts <- attempts + 1
    
    res <- tryCatch(
      expr = {
        wcl_events(
          report_code       = i_REPORT,
          fight_id          = i_FIGHT,
          data_type         = "All",
          hostility_type    = "Friendlies",
          filter_expression = "ability.id in (26635, 24907, 10060, 32182, 2825, 27165, 34919, 28508)",
          start_time = i_STARTTIME,
          end_time = i_ENDTIME
        )
      },
      error = function(e) {
        if (!exists("df_errors")) {
          df_errors <<- data.frame(
            i         = integer(),
            logID     = character(),
            fightID   = integer(),
            attempt   = integer(),
            error_msg = character(),
            timestamp = POSIXct(),
            stringsAsFactors = FALSE
          )
        }
        
        df_errors <<- dplyr::bind_rows(
          df_errors,
          data.frame(
            i         = i,
            logID     = i_REPORT,
            fightID   = i_FIGHT,
            attempt   = attempts,
            error_msg = e$message,
            timestamp = Sys.time(),
            stringsAsFactors = FALSE
          )
        )
        
        # Return the error object to check the message outside tryCatch
        return(e)
      }
    )
    
    # Check if the result was successful or an error was caught
    if (inherits(res, "error")) {
      perm_error_msg <- "Warcraft Logs GraphQL error: You do not have permission to view this report."
      
      if (grepl(perm_error_msg, res$message, fixed = TRUE)) {
        print(paste0("Permission denied for ", i_REPORT, " - skipping immediately to next report."))
        res <- NULL
        break # Exit while loop and move to next iteration of i
      } else if (attempts < max_retries) {
        print(paste0("Other error on iteration ", i, ". Waiting 50 minutes before retrying (Attempt ", attempts, " of ", max_retries, ")..."))
        res <- NULL
        Sys.sleep(3000)
      } else {
        res <- NULL
      }
    } else if (!is.null(res)) {
      success <- TRUE
    }
  }
  
  if (!is.null(res)) {
    df_events_buffs <- dplyr::bind_rows(df_events_buffs, res)
  }
  
  print(paste0(i, " out of ", N_FIGHTS, " - ", i_REPORT, " ", i_FIGHT))
}
  
write_csv(df_events_buffs,"./df_events_buffs.csv")
# df_events_buffs <- read_csv("./df_events_buffs.csv")
```
