---
title: "results"
date: "2026-08-10"
output: html_document
---

# Settings


```{r}
library(showtext)
library(ggtext)
library(extrafont)


font_add(family = "forgefooter", "forgefooter.ttf")
# font_import()
# n
showtext_auto(TRUE)

library(wclR)
library(tidyverse)
library(mgcv)
```

```{r}
df <- read_csv("./data/df_analysis.csv") %>%
  
  mutate(mage = factor(mage),
         boss = factor(boss),
         logID = factor(logID),
         
         # Ordinary factor for the mean differences
         vates = factor(
           vates,
           levels = c("0", "1","2+")
         ),
         
         # Ordered copy used ONLY for the duration interaction.
         # This makes 0 the reference curve.
         vates_by = ordered(
           vates_by,
           levels = c("0", "1","2+")
         )
  )
```

# FITTINGS

## - Fit All

```{r}
fit <- bam(amount ~ vates + ilvldiff + 
             
             s(mage, bs = "re")  + 
             s(logID, bs = "re") + NDruids + 
             
             Destruction + Berserking +
             PowerInfusion + uptime_pct + 
             VT + JoW +
             
             boss + 
             
             # Baseline duration-DPS relationship can differ by boss
             s(duration_s, by = boss,
               k = 10, id = "boss_duration") +
             
             # Additional duration-dependent effect of Innervate
             # relative to 0 Innervates
             s(duration_s, by = vates_by,
               k = 10, id = "inn_duration"),
           
           data = df, 
           method = "fREML", discrete = F)
```

```{r}
saveRDS(fit,"./data/fiting_all.RData")
```


```{r}
summary(fit)
gam.check(fit)
# concurvity(fit, full = TRUE)

```

## - Fit Conservative

```{r}
fit_conservative <- bam(amount ~ vates + s(mage, bs = "re") + boss + 
                          
                          s(duration_s, by = boss,
                            k = 20, id = "boss_duration") +
                          s(duration_s, by = vates_by,
                            k = 20, id = "inn_duration"),
                        
                        data = df, 
                        method = "fREML", discrete = F)
```

```{r}
saveRDS(fit_conservative,"./data/fit_conservative.RData")
```

```{r}
summary(fit_conservative)
gam.check(fit_conservative)
# concurvity(fit_conservative, full = TRUE)
```


## - Fit Adjusted

```{r}
fit_adjusted <- bam(amount ~ vates +  ilvldiff + NDruids + PowerInfusion +
                      s(mage, bs = "re") + 
                      boss + 
                      s(duration_s, by = boss,
                        k = 20, id = "boss_duration") +
                      
                      s(duration_s, by = vates_by,
                        k = 20, id = "inn_duration"),
                    
                    data = df, 
                    method = "fREML", discrete = F)
```

```{r}
saveRDS(fit_adjusted,"./data/fit_adjusted.RData")
```

```{r}
summary(fit_adjusted)
gam.check(fit_adjusted)
# concurvity(fit_adjusted, full = TRUE)
```


## - Fit Sensitivity

```{r}
fit_sensitivity <- bam(amount ~ vates +  VT + JoW +
                         s(mage, bs = "re") + 
                         boss + 
                         s(duration_s, by = boss,
                           k = 20, id = "boss_duration") +
                         s(duration_s, by = vates_by,
                           k = 20, id = "inn_duration"),
                       
                       data = df,
                       method = "fREML", discrete = F)
```

```{r}
saveRDS(fit_sensitivity,"./data/fit_sensitivity.RData")
```

```{r}
summary(fit_sensitivity)
gam.check(fit_sensitivity)
# concurvity(fit_sensitivity, full = TRUE)
```

## - Fit Final Model

The primary adjustment set was restricted to pre-encounter characteristics and external factors plausibly associated with both Innervate allocation and DPS. Variables that could themselves be affected by Innervate like consumable use, were evaluated separately in sensitivity analyses.

Log structure didn't do a thing

```{r}
fit_final_model <- bam(
  amount ~
    vates +
    ilvldiff + NDruids +
    PowerInfusion + uptime_pct + 
    boss +
    s(mage, bs = "re") +
    s(duration_s, by = boss,
      k = 10, id = "boss_duration") +
    s(duration_s, by = vates_by,
      k = 10, id = "inn_duration"),
  
  data = df,
  method = "fREML",
  discrete = F,
  
  control = gam.control(
    maxit = 500,
    trace = TRUE
  )
)

```

The estimated Innervate effect was robust to alternative model specifications, with similar effect curves across the minimally adjusted, confounder-adjusted, mana-adjusted, and fully adjusted models. Differences were primarily confined to longer fight durations, where observations were sparse and uncertainty was greater.

```{r}
summary(fit_final_model)
gam.check(fit_final_model)
concurvity(fit_final_model, full = TRUE)
```

```{r}
saveRDS(fit_final_model,"./data/fit_final_v1.RData")
```

## - Fit Final Model 2

The primary adjustment set was restricted to pre-encounter characteristics and external factors plausibly associated with both Innervate allocation and DPS. Variables that could themselves be affected by Innervate like consumable use, were evaluated separately in sensitivity analyses.

Log structure didn't do a thing

```{r}
fit_final_model_2 <- bam(
  amount ~
    vates +
    ilvldiff + NDruids +
    PowerInfusion + uptime_pct +
    VT +
    boss +
    s(mage, bs = "re") +
    s(duration_s, by = boss,
      k = 20, id = "boss_duration") +
    s(duration_s, by = vates_by,
      k = 20, id = "inn_duration"),
  
  data = df,
  method = "fREML",
  discrete = F,
  
  control = gam.control(
    maxit = 500,
    trace = TRUE
  )
)

```

The estimated Innervate effect was robust to alternative model specifications, with similar effect curves across the minimally adjusted, confounder-adjusted, mana-adjusted, and fully adjusted models. Differences were primarily confined to longer fight durations, where observations were sparse and uncertainty was greater.

```{r}
summary(fit_final_model_2)
gam.check(fit_final_model_2)
concurvity(fit_final_model_2, full = TRUE)
```

```{r}
saveRDS(fit_final_model_2,"./data/fit_final_v2.RData")
```



## - Fit Final Model 3

The primary adjustment set was restricted to pre-encounter characteristics and external factors plausibly associated with both Innervate allocation and DPS. Variables that could themselves be affected by Innervate like consumable use, were evaluated separately in sensitivity analyses.

Log structure didn't do a thing

```{r}
fit_final_model_3 <- bam(
  amount ~
    vates +
    ilvldiff + NDruids + Berserking + 
    PowerInfusion + uptime_pct +
    VT +
    boss +
    s(mage, bs = "re") +
    s(duration_s, by = boss,
      k = 20, id = "boss_duration") +
    s(duration_s, by = vates_by,
      k = 20, id = "inn_duration"),
  
  data = df,
  method = "fREML",
  discrete = F,
  
  control = gam.control(
    maxit = 500,
    trace = TRUE
  )
)

```

The estimated Innervate effect was robust to alternative model specifications, with similar effect curves across the minimally adjusted, confounder-adjusted, mana-adjusted, and fully adjusted models. Differences were primarily confined to longer fight durations, where observations were sparse and uncertainty was greater.

```{r}
summary(fit_final_model_3)
gam.check(fit_final_model_3)
concurvity(fit_final_model_3, full = TRUE)
```

```{r}
saveRDS(fit_final_model_3,"./data/fit_final_v3.RData")
```
